Runtime Feedback in a Meta-Tracing JIT for Efficient Dynamic Languages

### 2011-04-13 talk/icooolps2011/code/map.tex
change x = hint(x, promote=True) to just promote(x) to reduce confusion

    def getfield(self, name):
        map = hint(self.map, promote=True)
        index = map.getindex(name)
        if index != -1:
            return self.storage[index]
        return None

    def write_attribute(self, name, value):
        map = hint(self.map, promote=True)
        index = map.getindex(name)
        if index != -1:
            self.storage[index] = value
            return
        self.map = map.add_attribute(name)
        self.storage.append(value)

>>>>

    def getfield(self, name):
        map = self.map
        promote(map)
        index = map.getindex(name)
        if index != -1:
            return self.storage[index]
        return None

    def write_attribute(self, name, value):
        map = self.map
        promote(map)
        index = map.getindex(name)
        if index != -1:
            self.storage[index] = value
            return
        self.map = map.add_attribute(name)
        self.storage.append(value)

### 2011-04-13 talk/icooolps2011/code/version.tex
Typos and typographic details.
change x = hint(x, promote=True) to just promote(x) to reduce confusion

    def find_method(self, name):
        self = hint(self, promote=True)
        version = hint(self.version, promote=True)
        return self._find_method(name, version)

@@

    def change_method(self, name, value):
        self.methods[name] = value
        self.version = VersionTag()
\end{lstlisting}

>>>>

    def find_method(self, name):
        promote(self)
        version = self.version
        promote(version)
        return self._find_method(name, version)

@@

    def write_method(self, name, value):
        self.methods[name] = value
        self.version = VersionTag()
\end{lstlisting}
